---
title: "2024 US Presidential Election Forecast Model"
subtitle: "My subtitle if needed"
author: 
  - Viet Nguyen
  - Yihang Xu
  - Doran Wang
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(readr)
library(dplyr)
library(knitr)

clean_data <- read.csv("/Users/nguyenviet/Documents/term-paper-2/data/01-raw_data/clean_data.csv")

```


# Introduction

The 2024 U.S. Presidential Election Forecast Model aims to provide a comprehensive analysis of polling data to predict potential outcomes in the upcoming election. Utilizing a robust dataset that includes over 50 variables, such as pollster ratings, sample sizes, election dates, candidate affiliations, and polling methodologies, this model seeks to offer a nuanced understanding of voter preferences and trends across the country.

Key factors, such as pollster transparency scores, polling population characteristics, and election stages, are incorporated to ensure accuracy and relevance. By leveraging this data, the model can account for regional dynamics, partisan leanings, and shifts in voter sentiment, providing detailed insights into the evolving electoral landscape. This forecast model represents a data-driven approach to understanding the political climate as candidates navigate the road to the presidency.

# Data {#sec-data}


```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false
#| warning: false
#| message: false

ggplot(clean_data, aes(x = answer)) +
  geom_bar(fill = "red", color = "black") +
  labs(title = "Distribution of Answers", x = "Answer", y = "Count") +
  theme_minimal()
```

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

ggplot(clean_data, aes(x = answer, y = pct, fill = party)) +
  geom_bar(stat = "identity", color = "black") +
  labs(title = "Percentage of Support for Each Candidate", x = "Candidate", y = "Percentage") +
  theme_minimal() +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) + # Converts y-axis to percentage format
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Rotates x-axis labels
```



# Model

In the 2024 U.S. Presidential Election Forecast Model, the percentage of voter support for a candidate, represented by the variable pct, is modeled as the response variable. The predictors in this model include the candidate's political affiliation (party), the size of the sample surveyed (sample_size), the rating of the pollster based on their historical accuracy (numeric_grade), and the geographic location of the poll, represented by the variable state. By incorporating these predictors, the model aims to account for both the qualitative and quantitative factors that influence polling outcomes. The party variable captures the effect of political affiliation on voter support, while sample_size adjusts for the variability in poll precision. Numeric_grade reflects the reliability of the pollster, and state introduces regional variations in voting preferences. This model structure enables a detailed analysis of the factors driving election polling percentages across different states and political contexts.


## Model set-up
$$
\text{pct} = \beta_0 + \beta_1 \cdot \text{pollscore} + \beta_2 \cdot \text{sample size} + \beta_3 \cdot \text{numeric grade} + \epsilon
$$
where $\beta_0$ is the intercept, $\beta_1$, $\beta_2$, $\beta_3$, $\beta_4$ are the coefficients associated with the predictors, and $\epsilon$ represents the error term. This model accounts for both qualitative variables, like the party and state, as well as quantitative variables, such as sample size and pollster rating.

### Model justification
```{r}
#| echo: false
#| warning: false
#| message: false
model <- lm(pct ~ pollscore + sample_size + numeric_grade, data = clean_data)
summary(model)
```


# Results



# Discussion

# Appendix {-}


# References


