---
title: "2024 US Presidential Election Forecast Model"
subtitle: "My subtitle if needed"
author: 
  - Viet Nguyen
  - Yihang Xu
  - Doran Wang
thanks: "Code and data are available at: [https://github.com/vietng04/2024-US-Presidential-Election-Forecast](https://github.com/vietng04/2024-US-Presidential-Election-Forecast)."
date: today
date-format: long 
abstract: "This paper uses aggregate polling data and 'STH' modeling methods to predict the 2024 U.S. presidential election outcome. The Model use the factors related to the polls on Donald Trump’s support rate. The study also includes a deep-dive analysis of methodology on selected pollster, the New York Times (NYT), and then an idealized methodology and survey for predicting elections on a limited budget."
format: pdf
toc: true
toc-title: "Table of Contents"
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(readr)
library(dplyr)
library(knitr)

clean_data <- read_csv("../data/01-raw_data/clean_data.csv")
nyt_data <- read_csv("../data/02-analysis_data/NYT_data.csv")
```


# Introduction

The 2024 U.S. Presidential Election Forecast Model aims to provide a comprehensive analysis of polling data to predict potential outcomes in the upcoming election. Utilizing a robust dataset that includes over 50 variables, such as pollster ratings, sample sizes, election dates, candidate affiliations, and polling methodologies, this model seeks to offer a nuanced understanding of voter preferences and trends across the country.

Key factors, such as pollster transparency scores, polling population characteristics, and election stages, are incorporated to ensure accuracy and relevance. By leveraging this data, the model can account for regional dynamics, partisan leanings, and shifts in voter sentiment, providing detailed insights into the evolving electoral landscape. This forecast model represents a data-driven approach to understanding the political climate as candidates navigate the road to the presidency.

# Data {#sec-data}
The data used in this paper came from the FiveThirtyEight [@fivethirtyeight2024]. Data were cleaned and analyzed using the open source statistical programming language R [@citeR]. Libraries `tidyverse` [@citeTidyverse], `janitor` [@Citejan], `knitr` [@citeknitr], and `dplyr` [@citedplyr] were used for simulating, cleaning and testing. Graphics were made using `ggplot2` [@citeGG].


## Sample Data

```{r}
#| echo: false
#| eval: true
#| label: tbl-cleaned_data
#| tbl-cap: "Sample Cleaned Data"
#| warning: false

clean_data |>
  select(1:5) |>      # Select the first 3 columns
  head(5) |>
  kable(
    col.names = names(clean_data)[1:5],  # Automatically get the first 3 column names to match data
    booktabs = TRUE
  )
```

```{r}
#| label: fig-distribution_Answers
#| fig-cap: Distribution of Answers
#| echo: false
#| warning: false
#| message: false

ggplot(clean_data, aes(x = answer)) +
  geom_bar(fill = "red", color = "black") +
  labs(x = "Answer", y = "Count") +
  theme_minimal()
```

```{r}
#| label: fig-histogram_pct
#| fig-cap: Percentage of Support for Each Candidate
#| echo: false
#| warning: false
#| message: false

ggplot(clean_data, aes(x = answer, y = pct, fill = party)) +
  geom_bar(stat = "identity", color = "black") +
  labs( x = "Candidate", y = "Percentage") +
  theme_minimal() +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) + # Converts y-axis to percentage format
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Rotates x-axis labels
```



# Model

In the 2024 U.S. Presidential Election Forecast Model, the percentage of voter support for a candidate, represented by the variable pct, is modeled as the response variable. The predictors in this model include the candidate's political affiliation (party), the size of the sample surveyed (sample_size), the rating of the pollster based on their historical accuracy (numeric_grade), and the geographic location of the poll, represented by the variable state. By incorporating these predictors, the model aims to account for both the qualitative and quantitative factors that influence polling outcomes. The party variable captures the effect of political affiliation on voter support, while sample_size adjusts for the variability in poll precision. Numeric_grade reflects the reliability of the pollster, and state introduces regional variations in voting preferences. This model structure enables a detailed analysis of the factors driving election polling percentages across different states and political contexts.


## Model set-up
$$
\text{pct} = \beta_0 + \beta_1 \cdot \text{pollscore} + \beta_2 \cdot \text{sample size} + \beta_3 \cdot \text{numeric grade} + \epsilon
$$
where $\beta_0$ is the intercept, $\beta_1$, $\beta_2$, $\beta_3$, $\beta_4$ are the coefficients associated with the predictors, and $\epsilon$ represents the error term. This model accounts for both qualitative variables, like the party and state, as well as quantitative variables, such as sample size and pollster rating.

### Model justification
```{r}
#| echo: false
#| warning: false
#| message: false
model <- lm(pct ~ pollscore + sample_size + numeric_grade, data = clean_data)
summary(model)
```


# Results


# Discussion


\newpage


\appendix

# Appendix {-}

# Discussion of the survey’s methodology of Siena/NYT

## Population, Frame, and Sample

-Population:

-Frame:

-Sample:
a topline sample size of at least 100


## Sample Recruitment Method

## Sampling Approach's trade-offs

-Strengths:

-Weaknesses:


## How is non-response handled

## What is good and bad about the questionnaire

### Advantages

### Disadvantages


\newpage


# References


